Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-08-13 documentation/paper.tex
Added data table for waveform with wall cuts
Added and explained table for waveform with wall cut

During early tests with variations on $DeepConv(\omega)$, it was revealed to have a surprising and undesirable capacity to separate run types based on meaningless information. It was able to separate the AmBe calibration run from combined background runs with 96\% accuracy, and to separate all calibration runs from background runs with 91\% accuracy. This was determined to be caused by the network detecting and fitting on biases in the white noise at the beginning and hydraulic recompression sounds at the end of the raw waveform. This extraneous information was subsequently cropped out.

@@

!!!Include results with wall cuts!!!

@@

!!!TODO!!!

@@

This table shows that simple network architectures seem to produce better accuracy, likely due to reduced overfitting. Larger kernel sizes, more filters, and more layers make performance generally worse, while higher L2 regularization does the opposite. Dropout seems to have a weak correlation, possibly reducing accuracy slightly.

>>>>

During early tests with variations on $DeepConv(\omega)$ without $WallCut(D)$, it was revealed to have a surprising and undesirable capacity to separate run types based on meaningless information. It was able to separate the AmBe calibration run from combined background runs with 96\% accuracy, and to separate all calibration runs from background runs with 91\% accuracy. This was determined to be caused by the network detecting and fitting on biases in the white noise at the beginning and hydraulic recompression sounds at the end of the raw waveform. This extraneous information was subsequently cropped out.

@@

When $WallCut(D)$ was included, both accuracy and class-wise standard deviation improved drastically. The best configuration during a grid search was 96\% accurate and had a standard deviation of 0.41. This is better by both metrics than the multi-layer perceptron used in the original PICO-60 analysis.

@@

\begin{tabular}{|l|l|l|l|l|l|l|}
    \hline
    L2 $\lambda$ & Dropout & Filters & Kernel Size & \# Layers Multiplier & Max Accuracy & Class-Wise Std Dev \\
    \hline
    0.003 & 0 & 24 & 3 & 3 & 95\% & 0.44 \\
    \hline
    0.003 & 0 & 48 & 5 & 3 & 96\% & 0.41 \\
    \hline
    0.003 & 0.5 & 24 & 5 & 3 & 93\% & 0.50 \\
    \hline
    0.001 & 0 & 48 & 5 & 3 & 95\% & 0.48 \\
    \hline
    0.001 & 0.25 & 48 & 3 & 6 & 93\% & 0.62 \\
    \hline
    0.0003 & 0.5 & 24 & 5 & 6 & 95\% & 0.49 \\
    \hline
\end{tabular}

@@

These tables show that, both with and without $WallCut(D)$, simple network architectures seem to produce better accuracy, likely due to reduced overfitting. Larger kernel sizes, more filters, and more layers make performance generally worse, while higher L2 regularization does the opposite. Dropout seems to have a weak correlation, possibly reducing accuracy slightly.
